Get CRediT

### 2022-10-14 scripts/r/09_credit_taxonomy.Rmd
move timo to last, add emails

# Combine dfs in correct order
contributors <- bind_rows(initiators, analysts) %>% 
  mutate(middle_name = replace_na(middle_name, ""), 
         is_initiating = if_else(surname %in% initiating_authors, 1, 0)) %>% 
  unite(name, c("firstname", "middle_name", "surname"), sep = " ") %>% 
  mutate(name = str_replace_all(name, "  ", " "))

@@

There were `r nrow(contributors)` contributors from `r nrow(affiliations)` institutions. 
`r filter(affiliations, is.na(primary_affiliation)) %>% pull(n) %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation. 
There were `r filter(contributors, is.na(email_address)) %>% nrow` assholes that didn't include their email (`r filter(contributors, is.na(email_address)) %>% pull(name) %>% knitr::combine_words(words = .)`).

>>>>

# Combine dfs in correct order
contributors <- bind_rows(initiators, analysts) %>% 
  mutate(middle_name = replace_na(middle_name, ""),
    is_initiating = if_else(surname %in% initiating_authors, 1, 0)) %>% 
  unite(name, c("firstname", "middle_name", "surname"), sep = " ") %>% 
  mutate(name = str_replace_all(name, "  ", " ")) %>% 
  bind_rows(
    slice(., which(name != "Timo B. Roettger")), 
    slice(., which(name == "Timo B. Roettger"))
    ) %>%
  tail(nrow(.) / 2)

@@

There were `r nrow(contributors)` contributors from `r nrow(affiliations)` institutions. 
`r filter(affiliations, is.na(primary_affiliation)) %>% pull(n) %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation.
